Storm surge modelling in the Strait of Georgia

### 2014-10-14 RoughWork/manuscript.tex
Modified description of spatial extent of surge

The evolution and spatial distribution of the surge is highlighted in Figure \ref{fig:spatial} where the modelled residual is plotted every hour beginning on Dec 15 at 05:30 UTC. The surge enters the system from the Strait of Juna de Fuca and Johnstone Strait, peaking between Dec 15 at 6:30 and Dec 15 at 10:30 and then begins to subside throughout the entire domain. Notably, the Strait of Georgia experiences the largest surge values, upwards of 70 cm, whereas the Juan de Fuca region experiences a maximum surge around 55 cm. Additionally, the coastal areas on the mainland side of the Strait of Georgia experience slightly higher surges than the Vancouver Island side, likely due to the southerly wind in the atmospheric model pushing water against the mainland coast.

\begin{figure}
\centering
\includegraphics[scale=0.6]{Figures/dec2006_spatial.pdf}
\caption{Propagation of the storm surge on Dec 15 2006. Modelled residual every hour starting on Dec 15 at 05:30 UTC. Time advances from top left to bottom right. Wind vectors from the atmopsheric forcing are overlaid in black.}
\label{fig:spatial}
\end{figure}

>>>>

The evolution and spatial distribution of the surge is highlighted in Figure \ref{fig:spatial} where the modelled residual is plotted every hour beginning on Dec 15 at 05:30 UTC through to Dec 15 at 14:30 UTC. The surge enters the system from the Strait of Juna de Fuca, peaking between Dec 15 at 9:30 and Dec 15 at 11:30 and then begins to subside throughout the entire domain. Notably, the Strait of Georgia experiences the largest surge values, upwards of 60 cm, whereas the Juan de Fuca region experiences a maximum surge around 45 cm. Additionally, the coastal areas on the mainland side of the Strait of Georgia experience slightly higher surges than the Vancouver Island side, likely due to the southerly wind in the atmospheric model pushing water against the mainland coast. At about 11:30 UTC, the winds switch to northwesterly and then westerly, further amplifying the surge along the mainland coast.

\begin{figure}
\centering
\includegraphics[scale=0.6]{Figures/dec2006_spatial.pdf}
\caption{Propagation of the storm surge on Dec 15, 2006. Modelled residual every hour starting on Dec 15 at 05:30 UTC. Time advances from top left to bottom right. Wind vectors from the atmopsheric forcing are overlaid in black.}
\label{fig:spatial}
\end{figure}

An evaluation of the spatial distribution of the surge in a simulation without atmospheric forcing is provided in Figure \ref{fig:spatial_sshonly}. In this case, the surge amplitude across the Strait of Georgia, is uniform with no pronouced difference between the mainland side and Vancouver Island side. While the surge entering the domain from the Pacific Ocean is the leading order contribution, the winds may induce localized changes to the surge amplitude. Interestingly, the winds over the Strait of Juan de Fuca cause a decrease in surge amplitude in this region as the winds are acting to push the water towards the mainland.  Even without atmospheric forcing, there is still a siginificant difference in surge amplitude between the Strait of Georgria and the Strait of Juan de Fuca, perhaps because the Strait of Georgia is also affected by the surge entering the domain from Johnstone Strait at the northern boundary.
